---
title: "spicy"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{spicy}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Overview

coral contains a set of functions for:

- Listing variables of a data frame in three ways  
- Computing row means from a data.frame or matrix and dealing with NAs  

Functions `varlist()`, `varlist_shiny()` and `varlist_view()` contain descriptions of the attributes of each variable in the data frame. Rows are variables and columns are variable attributes (label, values, class, typeof, number of valid rows and NAs).

varlist(x, values = c("min_max", "all"), to_df = FALSE) creates a data frame of variables in source editor of RStudio.  

varlist_shiny(x, values = c("min_max", "all"), to_df = FALSE) creates an HTML table widget to display data frame of variables.

varlist_view(x, values = c("min_max", "all"), to_df = FALSE) creates a data frame of variables in viewer pane.

Function `mean_n(x, n)` computes row means from a data.frame or matrix. The first argument of `mean_n()` is variables (columns of a data frame or matrix) and the second argument a numeric value indicates the minimum amount of valid values (not NA) per row to calculate row mean (default = 1). Numeric value between 0 and 1 indicates a proportion of valid values per row to calculate the row mean.

Function `sum_n(x, n)` computes row sums from a data.frame or matrix. The first argument of `sum_n()` is variables (columns of a data frame or matrix) and the second argument a numeric value indicates the minimum amount of valid values (not NA) per row to calculate row sum (default = 1). Numeric value between 0 and 1 indicates a proportion of valid values per row to calculate the row sum.

Function `copy_write_excel(x)` copies a data frame or a matrix to the clipboard that can be pasted into Excel. 


```{r setup}
library(spicy)
```

Functions `varlist()`, `varlist_shiny()` and `varlist_view()` create a data frame of variables (list of variables) with descriptions of the attributes of each variable (label, values, class, typeof, number of valid rows and NAs).  

The argument `values = "min_max"` (default) displays minimum and maximum values of columns; `values = "all"` displays all values of columns.  

For `varlist(x)`, the argument `to_df = FALSE` (default) creates a data frame of variables in the source editor of RStudio; if TRUE, prints a tibble data format in the console.

```{r, eval = FALSE}
varlist(df)

```

```{r, eval = F}
df <- data.frame(Name = c("Jon", "Bill", "Maria", "Ben", "Tina"), Age = c(23, 41, 32, 58, 26))

varlist(df, to_df = TRUE)
varlist(df, values = "all", to_df = TRUE)
```

  
Installation

Latest version from GitHub :

```{r, eval = F}
library(devtools)

install_github("kocry/spicy")

# Alternative
library(remotes)

install_github("kocry/spicy")
```

